---
title: "lab-10-key"
author: "Thomas Lenihan"
date: "11/30/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(usethis)
library(janitor)

# install new libraries as well
library(beepr)
library(praise)
library(paletteer)
#library(sf) DOESNT WORK... --> https://r-spatial.github.io/sf/
library(cowsay)
```

Use the function `beep()` to indicate when a task is done

```{r eval = FALSE}

for (i in rev(seq(1:999))) (
  print(paste(i, "bottles of beer on the wall"))
) 

beepr::beep(5)

```

## praise and cowsay

packages built with a single purpose: to be kind and fun.

```{r}
praise("${Exclamation}, ${EXCLAMATION},...${exclamation}!!!!")

praise("Holy ${exclamation}, Batman - this code is ${ADJECTIVE}")
```

Use cowsay to make a character say something to you. 

```{r}
say("it's a series of tubes", by = "rms")
```

use `usethis::edit_r_profile()` to add processes/messages/time etc on Rstudio startup.

usethis::use_git()

usethis::use_github()

**for me, need to do this: `usethis::use_github(auth_token = "[here's where you put the PAT")`**


## paletteer to access thousands of color palettes

```{r}
storms %>% 
  group_by(name) %>% 
  summarize(min_pressure = min(pressure, na.rm = TRUE)) %>% 
  slice_min(n = 10, min_pressure) %>% 
  ggplot(aes(x = min_pressure, y = name))+
  geom_col(aes(fill = name))+
  scale_fill_paletteer_d("tvthemes::parksAndRec")

```


